NGO analysis

### 2022-08-01 Dashboard/NGO Analysis dashboard v006.Rmd
Deleting unnecessary tests. Formatting.

  ## scale maximum--------------------------------------------------------------
  # Reactive function to create the maximum value for revenue and expenses plots
  # the tests are probably not necessary, but included to be on the safe side
  maximum <- reactive({
    if (datatest() == TRUE || setequal(
      names(exceldata()),
      c("year", "firm", "category", "sub_category", "name", "value")
    )) {
      NA
    } else {
      excel_test() |>
        # removing the firm and sub-category columns
        select(-firm, -sub_category) |>
        # filtering to retain only revenue and expenses entries
        filter(category == "Revenue" | category == "Expenses") |>
        # grouping and summarising to calculate maximum value
        group_by(year, category) |>
        summarise(
          sum = sum(value, na.rm = TRUE)
        ) |>
        # Creating list of sums
        pull() |>
        # selecting the highest value
        max()
    }
  })

  ## Excel data test (also above)-----------------------------------------------
  # Reactive function to test for Excel data quality (basic)
  datatest <- reactive({
    # let me know if anyone has a better idea for testing
    if (mean(unlist(lapply(exceldata(), is.character))) != 0) {
      TRUE
    } else {
      FALSE
    }
  })

  ## Excel zero test------------------------------------------------------------
  excel_zero_check <- function(type) {
    excel_test() |>
      filter(
        category == as.character(all_of(type))
      ) |>
      summarise(
        zero = sum(value != 0, na.rm = TRUE)
      ) |>
      pull()
  }

@@

## zero_data_plot --------------------------------------------------------------

zero_data <- function() {
  empty_plot("All values are zero or missing.\nThis is unusual and may\nindicate a data problem.")
}

>>>>

  ## scale maximum--------------------------------------------------------------
  # Reactive function to create the maximum value for revenue and expenses plots
  maximum <- reactive({
      excel_test() |>
        # removing the firm and sub-category columns
        select(-firm, -sub_category) |>
        # filtering to retain only revenue and expenses entries
        filter(category == "Revenue" | category == "Expenses") |>
        # grouping and summarising to calculate maximum value
        group_by(year, category) |>
        summarise(
          sum = sum(value, na.rm = TRUE)
        ) |>
        # Creating list of sums
        pull() |>
        # selecting the highest value
        max()
  })

  ## Excel data test (also above)-----------------------------------------------
  # Reactive function to test for Excel data quality (basic)
  datatest <- reactive({
    # Testing if there are any characters instead of numbers (data probably
    # hopelessly corrupted)
    if (mean(unlist(lapply(exceldata(), is.character))) != 0) {
      TRUE
    } else {
      FALSE
    }
  })

  ## Excel zero test------------------------------------------------------------
  excel_zero_check <- function(type) {
    excel_test() |>
      # Choosing the specified category (i.e. Revenue or Expenses)
      filter(
        category == as.character(all_of(type))
      ) |>
      # Calculating if there are any zeroes
      summarise(
        zero = sum(value != 0, na.rm = TRUE)
      ) |>
      # just the single number
      pull()
  }

@@

## zero_data_plot --------------------------------------------------------------
zero_data <- function() {
  empty_plot(
    "All values are zero or missing.
    This is unusual and may
    indicate a data problem.")
}
